Model Order Redcution of Fluid Flow While Preserving Quadratic Invariants

### 2018-07-12 sections/5.res.tex
Add error in energy, mass and momentum conservation for KH example

>>>>

\begin{figure}
  \centering
  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{semilogyaxis}[ylabel = $\left|\mathbf{1}^T(\mathbf{r}-\mathbf{r}^r)(t)\right|$,
                 xlabel=$t$,
                 label style={font=\large},
                 legend pos=north east,
                 legend entries={$k=200$ ,$k=300$, $k=400$,$k=500$,$k=600$},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_200.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_300.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_400.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_500.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_600.txt};
    \end{semilogyaxis}%  
  \end{tikzpicture}
  \caption{}
  \label{mass_error_KH}
  \end{subfigure}\hfill
  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{semilogyaxis}[ylabel = $\left|(\mathbf{r}^{T}\mathbf{u}-\mathbf{r}^{rT}\mathbf{u}^{r})(t)\right|$,
                 xlabel=$t$,
                 label style={font=\large},
                 legend pos=north east,
%                 legend entries={$k=200$ Conv,$k=201$ Conv},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_200.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_300.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_400.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_500.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_600.txt};
    \end{semilogyaxis}%  
  \end{tikzpicture}
  \caption{}
  \label{momentum_error_KH}
  \end{subfigure}

  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{semilogyaxis}[ylabel = $\left| \dfrac{1}{2}\left( \mathbf{u}^{rT}\mathbf{R}^r\mathbf{u}^r-\mathbf{u}^{T}\mathbf{R}\mathbf{u}\right)\right|$,
                 xlabel=$t$,
                 label style={font=\large},
                 legend pos=north east,
%                 legend entries={$k=200$ Conv,$k=201$ Conv},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_200.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_300.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_400.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_500.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_600.txt};
    \end{semilogyaxis}%  
  \end{tikzpicture}
   \caption{}
  \label{energy_error_KH}
  \end{subfigure}
\caption{Comparison between the high fidelity solution of the Kelvin-Helmholtz problem and the reduced solution of the mass (\protect\subref{mass_error_KH}), the momentum (\protect\subref{momentum_error_KH}), and the total energy (\protect\subref{energy_error_KH}).}
\end{figure}
